\documentclass[12pt,a4paper,draft]{report}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\author{Frederik Appel Vardinghus-Nielsen}
\begin{document}
\noindent\textbf{Opgave 1}\\
The weather at a coastal resort is classified each day simply as "sunny" or "rainy". A sunny day is followed by another sunny day with probability 0.9 and a rainy day is followed by another rainy day with probability 0.3. \textbf{(a)} Describe this as a Markov chain. \textbf{(b)} If Friday is sunny, what is the probability that Sunday is also sunny? \textbf{(c)} If Friday is sunny, what is the probability that both Saturday and Sunday are sunny?\\\\
\textbf{(a)} Kæden beskrives med overgange. Lad solvejrsdag være 0 og regnvejrsdag være 1.
\begin{align*}
P_{00}=P(X_{n+1}=0/X_n=0)=0.9\\
P_{01}=P(X_{n+1}=1/X_n=0)=0.1\\
P_{11}=P(X_{n+1}=1/X_n=1)=0.3\\
P_{10}=P(N_{n+1}=0/X_n=1)=0.7
\end{align*}
\textbf{(b)} Opstil overgangsmatricen:
\begin{equation}
P=\begin{bmatrix}
0.9 & 0.1\\
0.7 & 0.3
\end{bmatrix}
\end{equation}
Sandsynligheden for at der er solvejrsdag søndag efter der er solvejrsdag fredag:
\begin{equation}
P_{00}^{(2)}=P^2_{ij}=0.88
\end{equation}
\textbf{(c)} Sandsynligheden for at der er solskinsvejr både lørdag og søndag givet at der er solskinsvejr fredag er $0.9^2$, da der lørdag er 0.9 sandsynlighed for det og der søndag, for der var solskin lørdag, er 0.9 sandsynlighed for at det er solskinsvejr.\\
Altså 0.81.\\\\
\textbf{Opgave 3}\\
A machine produces electronic components that may come out defective and the process is such that defective components tend to come in clusters. A defective component is followed by another defective component with probability 0.3, whereas a nondefective component is followed by a defective component with probability 0.01. Describe this as a Markov chain and find the long-term proportion of defective components.\\\\
Markovkæden beskrives ved overgange. Lad nondefekt være 0 og defekt være 1.
\begin{align*}
P_{00}=0.99\\
P_{01}=0.01\\
P_{11}=0.30\\
P_{10}=0.70
\end{align*}
$P$ opløftes i et højt tal for at finde grænseværdierne for indgangene i $P^n$ når $n\to\infty$. Der fås, at
\begin{equation}
P^n=\begin{bmatrix}
0.986 & 0.014\\
0.986 & 0.014
\end{bmatrix}.
\end{equation}
Altså er 1.4\% af produkterne defekte.\\\\
\textbf{Opgave 6}\\
Suppose that state $i$ is transient and that $i\to j$. Can $j$ be recurrent?\\\\
Ja - se korollar 8.2 og 8.3.\\\\
\textbf{Opgave 13}\\
Show that a limit distribution is a stationary distribution. The case of finite $S$ is easier, so you may assume this.











\end{document}