\documentclass[12pt,a4paper,draft]{report}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\author{Frederik Appel Vardinghus-Nielsen}
\begin{document}
\noindent\textbf{Opgave 94}\\
Let $X$ be lognormal with parameters $\mu=0$ and $\sigma^2=1$. Find \textbf{(a)} $P(X\leq 2)$, \textbf{(b)} $P(X^2\leq 2)$, \textbf{(c)} $P(X>E[X])$, and \textbf{(d)} the median $m$ of $X$.\\\\
\textbf{(a)} Gør som i eksempel 2.44
\begin{align*}
P(X\leq 2)=P(\log X\leq \log 2)=\Phi\left(\frac{\log 2-0}{\sqrt{1}}\right)\approx 0.755
\end{align*}
\textbf{(b)} Omskriv $X^2\leq 2$ til $X\leq \sqrt{2}$.
\begin{equation}
P(X\leq\sqrt{2})=P(\log X\leq\log \sqrt(2))=\Phi\left(\frac{\log(\sqrt{2})-0}{\sqrt{1}}\right)\approx 0.633
\end{equation}
\textbf{(c)} Beregn $E[X]$.
\begin{equation}
E[X]=\mathrm{e}^{0+1^2/2}=\mathrm{e}^{1/2}
\end{equation}
Beregn derefter $P(X\leq E[X])$.
\begin{equation}
P(X> \mathrm{e}^{1/2}=P(\log X>\log\mathrm{e}^{1/2})=1-P(\log X\leq\frac{1}{2})=1-\Phi\left(\frac{1}{2}\right)\approx 0.31
\end{equation}
\textbf{(d)} Medianen beregnes ved $\mathrm{e}^{\mu}$.
\begin{equation}
m=\mathrm{e}^{\mu}=\mathrm{e}^0=1
\end{equation}
\textbf{Opgave 73}\\
The element \textit{nobelium} has a half-life of 58 min. Let $X$ be the lifetime of an individual nobelium atom. Find \textbf{(a)} $P(X>30)$, \textbf{(b)} $P(X\leq 60|X>30)$, and \textbf{(c)} $E[X]$ and Var$[X]$.\\\\
\textbf{(a)} Find $\lambda$ ved hjælp af halveringstiden.
\begin{equation}
P(X>58)=\frac{1}{2}=\mathrm{e}^{-58\lambda}\,\Rightarrow\,\lambda=\frac{\log 2}{58}
\end{equation}
Beregn derefter $P(X>30)$.
\begin{equation}
P(X>30)=\mathrm{e}^{-30\log2/58}\approx 0.6987
\end{equation}
\textbf{(b)} Brug definition 1.4.
\begin{equation}
P(X<60|X\geq30)=\frac{P(X<60\cap X\geq30)}{P(X\geq40)}=\frac{\mathrm{e}^{\frac{-30\log2}{58}}-\mathrm{e}^{\frac{-60\log2}{58}}}{\mathrm{e}^{\frac{-30\log2}{58}}}\approx0.30127
\end{equation}
\textbf{(c)} Brug definitioner.
\begin{align*}
E[X]&=\frac{1}{\lambda}=\frac{58}{\log2}\approx83.7\\
\text{Var}[X]&=\frac{1}{\lambda^2}=\frac{58^2}{\log2^2}\approx7002
\end{align*}
\textbf{Opgave 81}\\\\
Two species of fish have weights that follow normal distributions. Species A has mean 20 and standard deviation 2; species B has mean 40 and standard deviation 8. Which is more extreme: a 24-pound A-fish or a 48-pound B-fish?\\\\
Der skal beregnes en Z-score.
\begin{equation}
Z=\frac{X-\mu}{\sigma}
\end{equation}
Jo højere Z-score, jo lavere sandsynlighed.
\begin{align*}
Z_A&=\frac{24-20}{2}=2\\
Z_B&=\frac{48-40}{8}=1
\end{align*}
En 24-punds A-fisk er mindst sandsynlig.\\\\
\textbf{Opgave 92}\\\\
Let $(X,Y)$ be uniformly distributed on the triangle with corners in $(0,0)$,$(0,1)$, and $(1,0)$. \textbf{(a)} Compute the correlation coefficient $\rho(X,Y)$. \textbf{(b)} If you have done (a) correctly, the value of $\rho(X,Y)$ is negative. Explain intuitively.\\\\
\textbf{(a)} Brug definitioner.
\begin{equation}
\rho(X,Y)=\frac{\text{Cov}[X,Y]}{\sqrt{\text{Var}[X]\text{Var}[Y]}}
\end{equation}
Kovarians beregnes.
\begin{align*}
\text{Cov}[X,Y]&=E[XY]-E[X]E[Y]=\int_0^1\!\int_0^{1-x}2xy\,dy\,dx-\int_0^1\!\int_0^{1-x}2x\,dy\,dx\\
&=\frac{1}{12}-\frac{1}{9}=-\frac{1}{36}
\end{align*}
Og varians.
\begin{align*}
\text{Var}[X]&=E[X^2]-(E[X])^2=\int_0^1\!\int_0^{1-x}2x^2\,dy\,dx-\left(\int_0^1\!\int_0^{1-x}\!2x\,dy\,dx\right)^2\\
&=\frac{1}{6}-\frac{1}{9}=\frac{1}{18}
\end{align*}
Slutteligt
\begin{equation}
\text{Cor}[X,Y]=\frac{-\frac{1}{36}}{\frac{1}{18}}=-\frac{1}{2}
\end{equation}
\textbf{(b)} Korrelationskoefficienten er negativ, da $y$ generelt aftager, når $x$ vokser.\\\\
\textbf{Opgave 107}\\
Let $(X,Y)$ be bivariate normal with means 0, variances 1, and correlation coefficient $\rho>0$, and let $U=X+Y,V=X-Y$. What is the joint distribution of $(U,V)$.









\end{document}