\documentclass[12pt,a4paper,draft]{report}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\author{Frederik Appel Vardinghus-Nielsen}
\begin{document}
\noindent\textbf{Opgave 137}\\
Let $X_1,X_2,\ldots$ be iid nonnegative and integer valued, and let $N\sim\text{Poi}(\lambda)$, independent of $X_k$. If the random sum $S_N=X_1+\ldots+X_N$ has a Poisson distribution with mean $\mu$, what is the distribution of $X_k$.\\\\
Beregn $G_X(s)$ ved
\begin{align*}
G_{S_N}&=\mathrm{e}^{\mu(s-1)}=\mathrm{e}^{\lambda(G_X(s)-1)}\\
&\Downarrow\\
G_X(s)&=\frac{\mu(s-1)}{\lambda}+1
\end{align*}
Siden $G_X(s)$ er et polynomium af grad 1, så har forsøget kun 2 forskellige resultater. Altså er det en Bernoullifordeling.\\\\
\textbf{Opgave 139}\\
Jobs arrive at a computer at a rate of 1.8 jobs/day. Each job requires an execution
time (in milliseconds) that has a binomial distribution with $n = 10$ and
$p = 0.5$ (where a zero execution time means that the job is rejected). Find
\textbf{(a)} the probability that the total execution time in a day for this type of job is at
least 2 ms, and \textbf{(b)} the expected total execution time in a day.\\\\
\textbf{(a)} Antag, at jobs/dag er Poissonfordelt. Altså haves
\begin{align*}
G_X(s)=(0.5+0.5s)^{10}\\
G_N(s)=\mathrm{e}^{1.8(s-1)}
\end{align*}
$G_X(s)$ sættes ind i $G_N(s)$.
\begin{equation}
G_{S_N}(s)=G_N(G_X(s))=\mathrm{e}^{1.8((0.5+0.5^{10})-1}
\end{equation}
Derefter beregnes sandsynligheden
\begin{equation}
P(S_N\geq 2)=\sum_{k=0}^1\frac{G_{S_N}'(0)}{k!}=0.831
\end{equation}
\\\\
\textbf{(b)} Find forventet værdi af binomialfordelingen og gang med 1.8.
\begin{equation}
1.8\,E[X]=1.8\,G'(1)=1.8\left((0.5+0.5s)^{10}\right)=9
\end{equation}
\textbf{Opgave 151}\\
Traffic accidents in a town occur according to a Poisson process at a rate of
two accidents per week. \textbf{(a)} What is the probability that a given day has no
accidents? \textbf{(b)} Whenever there is an accident, the risk is 1 in 10 that it will
cause personal injury. What is the probability that a given month has at least
one such accident? \textbf{(c)} Let N be the number of accident-free weeks in a year.
What is the distribution of N?\\\\
\textbf{(a)} Antal uheld pr. uge er Poissonsfordelt med $\lambda=2$. Antal uheld pr. dag er Poissonfordelt med $\mu=\frac{2}{7}$. Altså fås
\begin{equation}
P(X(1/7)=0)=\mathrm{e}^{-2/7}\frac{(2/7)^0}{0!}=0.75
\end{equation}
\textbf{(b)} Brug samme formel som før med $\lambda=2/10$ og $t=4$.
\begin{equation}
P(X(4)=0)=1-\mathrm{e}^{-8/10}\frac{-8/10^0}{0!}=0.55
\end{equation}
\textbf{Opgave 4}\\
Let $X_1,X_2,\ldots,X_n$ be i.i.d. random variables. The \textit{harmonic mean} is defined as
\begin{equation}
H_n=\left(\frac{1}{n}\sum_{k=1}^n\frac{1}{X_k}\right)^{-1}
\end{equation}
Suppose that the pdf of the $X_k$ is $f(x)=3x^2$, $0\leq x\leq1$, and find the limit of $H_n$ as $n\to\infty$.\\\\
Brug at
\begin{equation}
E[g(x)]=\int_0^1\!g(x)f_x(x)\,dx
\end{equation}
Altså
\begin{equation}
H_n\to E[g(x_k)]\text{ for }n\to\infty
\end{equation}
Så der haves
\begin{equation}
H_n=\int_0^1\!\frac{1}{x}3x^2\,dx=\frac{2}{3}\text{ for }n\to\infty
\end{equation}
\\\\
\textbf{Opgave 10}\\
In any given day, a certain email account gets a number of spam emails that has
a Poisson distribution with mean 200. What is the approximate probability that
it receives less than 190 spam emails in a day?\\\\

















\end{document}